Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space

### 2023-05-07 manuscript/manuscript.qmd
Use separate profiles + word count

---
title: "Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

@@

## References

>>>>

---
title: "Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"
short-title: "Amicable Contempt"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
---

@@

# References
